---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bmsma

<!-- badges: start -->
[![R-CMD-check](https://github.com/traitecoevo/bmsma/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/traitecoevo/bmsma/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/traitecoevo/bmsma/branch/master/graph/badge.svg)](https://app.codecov.io/gh/traitecoevo/bmsma?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of 'bmsma' is to ...

## Installation

'bmsma' is under active development. You can install the current developmental version of 'bmsma' from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("traitecoevo/bmsma")
```

## Quick demo

Fitting a classic linear regresion 
```{r example-ols}
library(bmsma)

x <- 
  bmsma_model("ols") |>
  bmsma_assign_data(X = Loblolly$age,
                   Y = Loblolly$height,
                   N = nrow(Loblolly)) |>
  bmsma_run()
```

Fitting an SMA line
```{r example-bsma}
library(bmsma)

x <- 
  bmsma_model("bsma") |>
  bmsma_assign_data(x = as.matrix(Loblolly[, c("age", "height")]),
                   n_obs = nrow(Loblolly)) |>
  bmsma_run()
```

Fitting a multi-level SMA line
```{r example-bsma}
library(bmsma)

x <- 
  bmsma_model("bmsma") |>
  bmsma_assign_data(x = as.matrix(Loblolly[, c("age", "height")]),
                   n_obs = nrow(Loblolly)) |>
  bmsma_run()
```

## Found a bug? 

Please submit a [GitHub issue](https://github.com/traitecoevo/bmsma/issues) with details of the bug. A [reprex](https://reprex.tidyverse.org/) would be particularly helpful with the bug-proofing process!  
